\documentclass[11pt,a4paper,sans,english]{moderncv}
\moderncvcolor{burgundy}
\moderncvstyle{classic}
\usepackage[utf8]{inputenc}
\usepackage[scale=0.8]{geometry}
\usepackage{babel}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\definecolor{dark-gray}{gray}{0.20}

%-------------------------------------------------------------
%            personal data
%-------------------------------------------------------------
\firstname{Samuele}
\familyname{Ferri}
\born{Varese, 20.01.1998}
\address{via Roigo 14, Cadro (Switzerland)}
\mobile{+41 76 452 2748}
\email{sferri1@uninsubria.it}
\homepage{ferrixio.github.io}
%\photo[90pt][0.4pt]{Fotoprofilo.jpg}


\begin{document}
	\makecvtitle
	\vspace{-1cm}
	\section{Education}
	\cventry{2024--now}{PhD in Computer science and Mathematics of Computation}{University of Insubria}{Como}{}{}
	\cventry{2020--2022}{Master degree in mathematics}{University of Insubria}{Como}{}{Graduation grade: 104/110}
	\cventry{2022}{Teaching qualification (Italy)}{University of Insubria}{Como}{}{24 cfu qualification}
	\cventry{2017--2020}{Bachelor degree in mathematics}{University of Insubria}{Como}{}{Graduation grade: 93/110}
	\cventry{2013--2017}{High school diploma}{Liceo Lugano 1}{Lugano}{}{}
	
	\vspace{0.25cm}
	
	\subsection{Research interests}
	\cvitem{}{Numerical linear algebra, Numerical methods for PDEs}

	\section{Master thesis}
	\cvitem{Title}{\emph{De exoticis 7-sphaeris}}
	\cvitem{Supervisor}{Giovanni Bazzoni}
	\cvitem{Description}{In this paper, we retrace Milnor's studies aimed at finding homeomorphic but not diffeomorphic manifolds on the 7-sphere, through the study of 3-sphere bundles on the 4-sphere and their characteristic classes.}
	
	\section{Bachelor thesis}
	\cvitem{Title}{\emph{Mixing time for Glauber dynamics}}
	\cvitem{Supervisor}{Andrea Posilicano}
	\cvitem{Description}{This thesis work is aimed at studying the time required for the Markov chain describing the Glauber dynamics for the Ising model to reach its stationary distribution.}

	
	\section{Experiences}
	\cventry{2026}{Internship}{Università della Svizzera Italiana}{Lugano}{}{From January to July.}
	\cventry{2025-2026}{Tutoring}{University of Insubria}{Como}{}{Covered the role of disciplinary tutor for the first year of the bachelor's degree in mathematics.}
	\cventry{2025}{Internship}{Institute for applied mathematics "Mauro Picone"}{National Research Council of Italy}{Rome}{From January to July.}
    \cventry{2024-2025}{Tutoring}{University of Insubria}{Como}{}{Covered the role of disciplinary tutor for the first year of the bachelor's degree in mathematics.}
	\cventry{2024}{Tutoring}{University of Insubria}{Como}{}{Covered the role of tutor for the "\textit{Analisi 2}" course of the bachelor's degree in mathematics.}
	\cventry{2024}{Tutoring}{University of Insubria}{Como}{}{Covered the role of tutor for the "\textit{Matematica 2}" course of the bachelor's degree in chemistry.}
	\cventry{2023}{Data analyst}{Tools for Smart Minds}{Castel Mella (BS)}{}{Covered this role from June to December.}
	\cventry{2023}{Substitution}{Canobbio Middle School}{Canobbio}{}{Substitute for maths lessons for a first grade.}
	\cventry{2023}{Substitution}{Centro Professionale di Trevano}{Canobbio}{}{Substitute three teachers for mathematics for vocational baccalaureate classes.}
	\cventry{2023}{Substitution}{Liceo Lugano 1}{Lugano}{}{Substitute for two teachers for mathematics and computer science.}
	\cventry{2022}{Substitution}{Canobbio Middle School}{Canobbio}{}{Substitute for basic maths lessons for a third and a fourth grade.}
	\cventry{2021--2022}{Tutoring}{University of Insubria}{Como}{}{Covered the role of tutor for the "\textit{Geometria 2}" course of the bachelor's degree in mathematics.}
	
	\section{Languages}
	\cvitem{Mother t.}{Italian}
	\cvitem{Advanced}{English}
	\cvitem{Basic}{German, French}
	
	\section{Computer skills}
	\cvitem{Advanced}{Python, \LaTeX, C++, Matlab}
	\cvitem{Intermediate}{HTML, CSS, C\#, SQL, LabView}
	\cvitem{Basic}{Javascript, Java}
	
	\section{Pubblications}
	\cvitem{}{N. Barakitis, M. Donatelli, S. Ferri, V. Loi, S. Serra-Capizzano, R. Sormani. (2025). "\emph{Blocking structures, approximation, and preconditioning}". Numerical Algorithms. 1-35. 10.1007/s11075-025-02157-y}
	
	\cvitem{}{S. Ferri, C. Giraudo, V. Loi, M. Kuchta, S. Serra-Capizzano. "\emph{Spectral analysis of the stiffness matrix sequence in the approximated Stokes equation}". (preprint, doi.org/10.48550/arXiv.2510.25252)}
		
	\vfill
	\today
	
	I authorise the processing of my personal data pursuant to Law 196/03 and art.13 GDPR 679/13.	
\end{document}